Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-27 WSSSPE3/report/wg_appendix_publishing_SW.tex
small changes to changes

\item KBase: narratives built on IPython\slash Jupyter notebooks; to build
publications that are reproducible, and can be commented or annotated.

@@

The group also discussed future possibilities for a new publication format
which might provide advantages:
\begin{itemize}

@@

\item RIO is an effort to publish fragmentary results that can subsequently be
combined into a single content item. \choinote{What's RIO?}

>>>>

\item KBase: narratives build on IPython\slash Jupyter notebooks to build
publications that are reproducible, and can be commented or annotated.

@@

The group also discussed future possibilities for a new publication format
that might provide advantages:
\begin{itemize}

@@

\item The Research Ideas and Outcomes (RIO) journal is an effort to publish fragmentary results that can subsequently be
combined into a single content item.
